### 2018-01-31 ApproxComp/sec-beyond.tex

\section{Beyond Query and Data Approximations}
\label{sec-beyond}

  For big data analytics, there are no one-size-fits-all techniques.  it is often necessary to combine different techniques to obtain good solutions.

@@

It is also obvious that techniques beyond query and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.

>>>>

\section{Beyond Query and Data Approximation}
\label{sec-beyond}

  For big data analytics, there are no one-size-fits-all techniques, and it is often necessary to combine different techniques to obtain good solutions.

@@

It is also obvious that techniques beyond query approximation and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.
